Measurement and Probability in Fuzzy Quantum Theories

### 2017-06-25 prop_iop.tex
prop_iop.tex \subsection{From Real-valued to Interval-valued} Updating..

\begin{lemma}Consider a set of intervals\nb$\mathscr{I}$ with an
additive interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$.
For any normalized pure state\nb$\ket{\phi}$, $\iota\circ\mu_{\phi}^{\mathrm{\mathrm{B}}}$
is a quantum IVPM such that $\mathrm{core}\left(\iota\circ\mu_{\phi}^{\mathrm{\mathrm{B}}}\right)$
has an unique element. Obviously, if $\iota$ is convex, so does $\iota\circ\mu_{\phi}^{\mathrm{\mathrm{B}}}$.\end{lemma}

\begin{proof}$\left(\iota\circ\mu_{\phi}^{\mathrm{\mathrm{B}}}\right)\left(\proj{\phi}\right)=\iota\left(\mu_{\phi}^{\mathrm{\mathrm{B}}}\left(\proj{\phi}\right)\right)=\iota\left(1\right)=\left[1,1\right]$,
i.e., for any quantum probability measure~$\mu\in\mathrm{core}\left(\iota\circ\mu_{\phi}^{\mathrm{\mathrm{B}}}\right)$,
we have $\mu\left(\proj{\phi}\right)=1$. Therefore, $\mu=\mu_{\phi}^{\mathrm{\mathrm{B}}}$.\end{proof}

@@

@@

\begin{proof}By definition, we have
\begin{equation}\eqalign{ 
 & \rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)\\ 
\Leftrightarrow & \forall P\in\events\ \mu_{\rho}^{\mathrm{B}}\left(P\right)\in\iota\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)\\ 
\Rightarrow & \forall\textrm{ normalized pure state }\ket{\psi}\ \mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\in\iota\left(\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right) 
}\end{equation}
\end{proof}

>>>>

\begin{lemma}Consider a set of intervals\nb$\mathscr{I}$ with an
additive interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$.
For any normalized pure state\nb$\ket{\phi}$, $\iota\circ\mu_{\phi}^{\mathrm{\mathrm{B}}}$
is a quantum IVPM such that $\coreBorn\left(\iota\circ\mu_{\phi}^{\mathrm{\mathrm{B}}}\right)$
has an unique element. Obviously, if $\iota$ is convex, so does $\iota\circ\mu_{\phi}^{\mathrm{\mathrm{B}}}$.\end{lemma}

\begin{proof}$\left(\iota\circ\mu_{\phi}^{\mathrm{\mathrm{B}}}\right)\left(\proj{\phi}\right)=\iota\left(\mu_{\phi}^{\mathrm{\mathrm{B}}}\left(\proj{\phi}\right)\right)=\iota\left(1\right)=\left[1,1\right]$,
i.e., for any quantum probability measure~$\mu\in\coreBorn\left(\iota\circ\mu_{\phi}^{\mathrm{\mathrm{B}}}\right)$,
we have $\mu\left(\proj{\phi}\right)=1$. Therefore, $\mu=\mu_{\phi}^{\mathrm{\mathrm{B}}}$.\end{proof}

@@

\begin{definition}\cite{RobertsVarberg1973,peres1995quantum,544199}Given
a operator or matrix\nb$\rho$, the norm of $\rho$ is defined by
\begin{equation}
\left\Vert \rho\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho}{\psi}\right|\,.
\end{equation}
\end{definition}

@@

\begin{proof}By definition, we have $\mu_{\rho'}^{\mathrm{B}}\left(P\right)\in\iota\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)$
for all $P\in\events$. By substitute $P=\proj{\psi}$, we have 
\begin{equation}
\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\in\iota\left(\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right)\,.\label{eq:consistent2another_state}
\end{equation}
Since the maximum length of intervals in $\mathscr{I}$ is $1/n$,
we can move $\rho$ and $\rho'$ to the same side and rewrite equation~(\ref{eq:consistent2another_state})
as
\begin{equation}
\frac{1}{n}\ge\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho'-\rho}{\psi}\right|\,.
\end{equation}
Applying maximum on both side, we have
\begin{equation}
\frac{1}{n}\ge\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho'-\rho}{\psi}\right|=\left\Vert \rho'-\rho\right\Vert \,.
\end{equation}
\end{proof}

Previously, we proved that if $\rho'$ is consistent with $\iota\circ\mu_{\rho}^{\mathrm{B}}$,
then $\rho'$ is close to $\rho$. Conversely, if $\rho'$ is close
to $\rho$, $\rho'$ is consistent with $\iota\circ\mu_{\rho}^{\mathrm{B}}$
by the following lemma.

\begin{lemma}Given a Hilbert space with the set of all projectors\nb$\events$,
and an interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
with the minimum length of intervals in $\mathscr{I}\backslash\left\{ \imposs,\necess\right\} $
is $1/n$. For two mixed state\nb$\rho$ and $\rho'$, if the following
conditions holds.
\begin{itemize}
\item $\left\Vert \rho-\rho'\right\Vert \le1/n$.
\item $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\imposs$ if and only if $P=\mathbb{0}$.
\item $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\necess$ if and only if $P=\mathbb{1}$.
\end{itemize}
Then, $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.\end{lemma}

\begin{proof}Since
\begin{equation}
\frac{1}{n}\ge\left\Vert \rho'-\rho\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho'-\rho}{\psi}\right|\,,
\end{equation}
we have
\begin{equation}
\frac{1}{n}\ge\left|\melem{\psi}{\rho'-\rho}{\psi}\right|=\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|
\end{equation}
for all normalized pure state\nb$\ket{\psi}$. \end{proof}
